\documentclass[11pt,twocolumn,a4paper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{pifont}
\pagestyle{empty}
\parindent0pt
\parskip3pt
\title{Apple Pie\\\small Apfel Gitterkuchen}
\author{Markus Gutschke}
\date{\ }
\begin{document}
\maketitle
\thispagestyle{empty}
\textit{
\begin{tabular}{ll}
$1\over2$lb&flour\\
$1\over4$lb&butter\\
5 Tbsp&sugar\\
1&egg\\
$\diamond$&\\
5&Granny Smith apples\\
5 Tbsp&sugar\\
3 Tbsp&lemon juice\\
$\frac12$ cup&chopped almonds\\
$\frac12$ cup&raisins\\
$\frac12$ tsp&ground cinnamon\\
\end{tabular}}

\leavevmode\vbox to .2in{\vss}

Preheat oven to $360^{\circ}$F.

Mix the flour, butter, sugar, and egg. If the dough is too dry, add a
small quantity of water; if it is too sticky, add some more flour.
Set aside about a quarter of the dough for the top. Fill the rest of
the dough into a spring form (spread a thin layer of butter onto the
form to prevent the dough from sticking).

Peel the apples and cut into 1'' pieces. Add sugar, lemon juice,
almonds, raisins, and cinnamon. Mix thoroughly. Fill into ontop of the 
dough.

Roll out strands of dough and weave into a lattice to cover the apples.

Bake for about 1 hour until the dough turns a light brown.
\vfill
\textit{
\begin{tabular}{ll}
250g&Mehl\\
125g&Butter\\
65g&Zucker\\
1&Ei\\
$\diamond$&\\
5&Granny Smith \"Apfel\\
5 Tl&Zucker\\
3 Tl&Zitronensaft\\
3 Tl&gehackte Mandeln\\
3 Tl&Rosinen\\
$\frac12$ tl&gemahlener Zimt\\
\end{tabular}}

\leavevmode\vbox to .2in{\vss}

Den Ofen auf $180^{\circ}$C vorheizen.

Das Mehl mit der Butter, dem Zucker und dem Ei verkneten. Falls der
Teig zu trocken erscheint, eine kleine Menge Wasser hinzuf\"ugen;
falls er zu klebrig ist, etwas mehr Mehl dazugeben. Ein Viertel des
Teigs f\"ur die Abdeckung zur Seite legen. Den \"ubrigen Teig in eine
Springform geben (die Form vorher mit Butter ausstreichen, um zu
verhindern, da\ss\ der Teig anhaftet).

Die \"Apfel sch\"alen und in zentimetergro\ss e St\"ucke
schneiden. Zucker, Zitronensaft, Mandeln, Rosinen und Zimt dazugeben
und gr\"undlich durchr\"uhren. Die \"Apfel auf den Teig geben.

Teigstr\"ange ausrollen und zu einem Gitter verweben, mit dem der
Kuchen abgedeckt wird.

Den Kuchen etwa eine Stunde backen bis der Teig leicht braun wird.

\end{document}
