\documentclass[11pt,twocolumn,a4paper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{pifont}
\pagestyle{empty}
\textheight1.1\textheight
\parindent0pt
\parskip3pt
\title{Black Bean Stew\\ \small (Schwarze-Bohnen Eintopf)}
\author{Markus Gutschke}
\date{\ }
\begin{document}
\maketitle
\thispagestyle{empty}
\textit{
\begin{tabular}{ll}
$4$&carrots\\
$1$&potato\\
$\frac18$&celery root\\
$1$ clove&garlic\\
$1$&onion\\
$2$ Tbsp&olive oil\\
&bacon\\
$1 \frac12$lb&beef\\
$2$ cups&dried black beans\\
$1 \frac12$ cups&port wine\\
$1 \frac12$ cups&red wine\\
4&red or green peppers\\
&cream\\
&red paprika powder\\
&cilantro\\
&tomato ketchup\\
\end{tabular}}

\leavevmode\vbox to .2in{\vss}

Over night, soak beans in part of the port wine.

Chop the carrots, potatoes, celery root, garlic, and onion into very
small pieces and fry in olive oil. When the onions turn golden brown,
take the vegetables out of the pot. Dice the bacon and fry until it
starts turning brown. Cut the beef into 1'' pieces, add to the bacon
and fry at high temperature. Return vegetables back into the pot. Add
beans, finely chopped peppers, and diced tomato. Simmer four hours on
low heat. Keep adding port and red wine regularly.

Take off the stove and add cream. Add red paprika, cilantro, and
tomato ketchup to taste.

\vfill\eject

\textit{
\begin{tabular}{ll}
$4$&M\"ohren\\
$1$&Kartoffel\\
$\frac18$&Sellerieknolle\\
$1$ Zehe&Knoblauch\\
$1$&Zwiebel\\
$2$ Tl&Oliven\"ol\\
&ger\"aucherter Speck\\
750g&Rindsgulasch\\
$200$ml&getrocknete schwarze Bohnen\\
$150$ml&Portwein\\
$150$ml&Rotwein\\
4&Pfefferonie\\
&Sahne\\
&roter Paprika\\
&frischer Coriander\\
&Tomatenketchup\\
\end{tabular}}

\leavevmode\vbox to .2in{\vss}

Die Bohnen \"uber Nacht in einem Teil des Portweins einweichen.

Die M\"ohren, die Kartoffel, den Sellerie, den Knoblauch und die Zwiebel
fein hacken und in Oliven\"ol anbraten. Wenn die Zwiebeln goldgelb sind,
das Gem\"use aus dem Topf nehmen, die Speckw\"urfel auslassen und in dem
Fett das in kleine St\"ucke geschnittene Fleisch scharf anbraten. Das
Gem\"use, die eingeweichten Bohnen, die fein gehackten Pfefferonie und
die kleingeschnittene Tomate dazugeben. F\"ur vier Stunden auf kleiner
Flamme kochen, bis die Bohnen weich werden. Regelm\"a\ss ig mit Rotwein und
Portwein immer soviel Fl\"ussigkeit nachf\"ullen, da\ss\ die Bohnen nicht
anbrennen.

Zum Schluss die Sahne dazugeben und mit Salz, roter Paprika, frischem
Coriander und Tomatenketchup abschmecken.

\end{document}
