\documentclass[11pt,twocolumn,a4paper]{article}
\usepackage{times}
\usepackage{helvet}
\usepackage{pifont}
\pagestyle{empty}
\parindent0pt
\parskip3pt
%
\makeatletter
\let\otitle\title
\let\oauthor\author
\let\omaketitle\maketitle
\let\o@maketitle\@maketitle
\def\maketitlepage{
  \let\title\otitle
  \let\author\oauthor
  \let\maketitle\omaketitle
  \let\@maketitle\o@maketitle}
\makeatother
\date{\ }
%
\begin{document}
\title{Canneloni}
\author{Markus Gutschke}
\maketitle
\thispagestyle{empty}
\textit{
\begin{tabular}{ll}
\multicolumn{2}{l}{\textbf{Pasta Dough}}\\
2 cups&flour\\
3&eggs\\
1 tsp&salt\\
1 Tbsp&olive oil\\
\multicolumn{2}{l}{\textbf{B\'echamel Sauce}}\\
1 oz&butter\\
2 Tbsp&flour\\
2$1\over2$ cups&milk\\
3 Tbsp&Parmesan cheese\\
\multicolumn{2}{l}{\textbf{Marinara Sauce}}\\
2 Tbsp&olive oil\\
$1\over2$&small onion\\
1 oz&bacon\\
14 oz&canned tomatoes\\
$1\over2$ cups&frozen peas\\
1&bell pepper\\
1 Tbsp&oregano\\
1 Tbsp&red paprika\\
1 Tbsp&A1 sauce\\
2 Tbsp&ketchup\\
1 fl oz&gin\\
\multicolumn{2}{l}{\textbf{Canneloni}}\\
4 oz&Mozarella cheese\\
3 oz&Prosciutto\\
1 oz&dried Porcini mushrooms\\
1 Tbsp&bread crumbs\\
\end{tabular}}

\leavevmode\vbox to .3in{\vss}

Soak the Porcini mushrooms in water and set aside.

Blend the flour, eggs, salt, and olive oil in a food processor until
mixture begins to form a ball. Knead on a floured surface folding in
additional flour as needed. Roll out the dough with a rolling pin,
sprinkle with some more flour, fold and set aside.

Make a roux from the butter and flour. Add milk, stir until smooth,
add the Parmesan cheese and cook for another minute. Set aside.

Add the finely chopped onions and cubed bacon to the olive oil and fry
at medium heat until the onions turn a light brown color. Add the
canned tomatoes, the peas, the chopped bell pepper and the spices.
Cook for about 10min. Drain the water from the Porcini mushrooms and
add it together with the gin to the Marinara sauce.  Set aside.

Unfold the pasta dough unto a floured surface. Pour about half of the
B\'echamel sauce onto the dough and spread evenly. Cover with Prosciutto
and Porcini mushrooms. Add about four table spoons of Marinara
sauce. Chop the Mozarella cheese and sprinkle about one fourth onto
the pasta. Grab one side of the pasta and carefully roll it up.

Preheat the oven to $340^{\circ}$F.

Fill the remaining Marinara sauce into an 8''$\times$4'' pan. Cut 1'' to
1$1\over2$'' thick slices off the rolled up pasta and set them into the
pan. Cover the slices with the remaining Mozarella cheese and sprinkle
the bread crumbs on top. Evenly distribute the remaining B\'echamel
sauce over the pasta.

Bake for about 45min or until the top turns a light brown.

Serves 4.

\clearpage
\maketitlepage
\title{Canneloni}
\author{Markus Gutschke}
\maketitle
\thispagestyle{empty}
\textit{
\begin{tabular}{ll}
\multicolumn{2}{l}{\textbf{Nudelteig}}\\
150g&Mehl\\
3&Eier\\
1 Tl.&Salz\\
1 E\ss l.&Oliven \"Ol\\
\multicolumn{2}{l}{\textbf{B\'echamel Sauce}}\\
30g&Butter\\
2 E\ss l.&Mehl\\
$1\over2$l&Milch\\
3 E\ss l.&Parmesan\\
\multicolumn{2}{l}{\textbf{Marinara Sauce}}\\
2 E\ss l.&Oliven \"Ol\\
$1\over2$&kleine Zwiebel\\
30g&durchwachsener Speck\\
400ml&eingelegte Tomaten\\
80g&tiefgefrorene Erbsen\\
1&gr\"une Paprikaschote\\
1 E\ss l.&Oreganum\\
1 E\ss l.&Roter Paprika\\
1 E\ss l.&A1 Sauce\\
2 E\ss l.&Ketchup\\
30cc&Gin\\
\multicolumn{2}{l}{\textbf{Canneloni}}\\
100g&Mozarella\\
80g&Prosciutto\\
30g&getrocknete Steinpilze\\
1 E\ss l.&Paniermehl\\
\end{tabular}}

\leavevmode\vbox to .3in{\vss}

Die Steinpilze in Wasser einweichen und zur Seite stellen.

Mehl, Eier, Salz und Oliven\"ol in der K\"uchenmaschine vermengen bis
sich der Teig vom Boden l\"ost. Auf einer eingemehlten Arbeitsfl\"ache
den Teig kneten und nach Bedarf Mehl hinzuf\"ugen. Den Teig mit dem
Nudelholz d\"unn ausrollen, mit Mehl bestreuen, zusammenfalten und zur
Seite stellen.

Aus Butter und Mehl eine helle Einbrenne erstellen. Die Milch
hinzuf\"ugen und glattr\"uhren. Den Parmesan unterr\"uhren und noch
eine Minute kochen; danach zur Seite stellen.

Die kleingehackten Zwiebeln mit dem gew\"urfelten Speck in Oliven\"ol
bei mittlerer Hitze anbraten bis die Zwiebeln sich leicht braun
f\"arben. Die Tomaten, Erbsen, die gehackte Paprikaschote und die
Gew\"urze dazugeben. Weitere 10min kochen. Das Wasser von den
Steinpilzen abgie\ss en und mit dem Gin zur Sauce geben. Die Marinara
Sauce zur Seite stellen.

Den Nudelteig auf einer gemehlten Arbeitsfl\"ache ausbreiten. Etwa
die H\"alfte der B\'echamel Sauce gleichm\"a\ss ig auf dem Teig
verstreichen. Mit Prosciutto und Steinpilzen abdecken. Etwa vier
E\ss l\"offel Marinara Sauce \"uber die Nudeln verteilen. Den
Mozarellak\"ase kleinhacken und ein Viertel \"uber die Nudeln
geben. Eine Seite des Teigs greifen, und ihn vorsichtig
zusammenrollen.

Den Ofen auf $170^{\circ}$C vorheizen.

Die restliche Marinara Sauce in eine gro\ss e Auf\-lauf\-form
f\"ullen. 3cm bis 4cm dicke Scheiben von den aufgerollten Nudel
abschneiden und in die Auflaufform geben. Die Scheiben mit dem
restlichen Mozarella bedecken und mit Paniermehl bestreuen. Die Nudeln
mit der restlichen B\'echamel Sauce gleichm\"a\ss ig abdecken.

Etwa 45min backen bis die Canneloni eine hellbraune Kruste haben.

Ergibt 4 Portionen.
\end{document}
